Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-11-21 5_results_discussions/coselog-wabo/coselog-wabo.tex
Remove itemize in discussion

\begin{itemize}
  \item In \textit{Process Model Mining} stage, with 10 \% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values. 
  \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases for most of the cases. When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process models compared to others, fail in spotting mismatch patterns under \textit{graph-edit similarity}.
  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points. For instance, cluster of Municipality \#1 performs worse in 6 indicators with the difference of 25 \% and on average 5 mismatch patterns are listed for each performance indicator. When it is compared to the total mismatch patterns of Municipality \#1, which is 357, proposed approach helps significantly to the user for focusing performance improvement.
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-generation-analysis-k3}
		\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
	  \label{fig:coselog-wabo-recommendation-generation-analysis}
	\end{figure}
\end{itemize}

>>>>

In \textit{Process Model Mining} stage, with 10 \% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values. In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster. In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases for most of the cases. When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process models compared to others, fail in spotting mismatch patterns under \textit{graph-edit similarity}. In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points. For instance, cluster of Municipality \#1 performs worse in 6 indicators with the difference of 25 \% and on average 5 mismatch patterns are listed for each performance indicator. When it is compared to the total mismatch patterns of Municipality \#1, which is 357, proposed approach helps significantly to the user for focusing performance improvement.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-generation-analysis-k3}
	\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
  	\label{fig:coselog-wabo-recommendation-generation-analysis}
\end{figure}

### 2015-11-21 5_results_discussions/loan-application-process/loan-application-process.tex
no message
Remove itemize in discussion

\begin{itemize}
  \item In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.
  \item In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators. In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster. 
  \item In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization. As the similarity between process models decreases our method spots more mismatch patterns and it ensures that the developed mismatch pattern analyzers work as expected for this dataset. 
  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}. 
    \begin{figure}
    	\centering
    	\includegraphics[width=\textwidth]{5_results_discussions/loan-application-process/recommendation-generation-analysis}
    	\caption{Recommendation Generation analysis for Loan Application Process dataset}
      \label{fig:loan-recommendation-generation-analysis}
    \end{figure}
  In order to construct the data in Figure~\ref{fig:loan-recommendation-generation-analysis}, every organization is selected one-by-one with different threshold values. For each analysis, number of performance indicators and average number of mismatch patterns causing them are plotted. In addition, total number of mismatch patterns without clustering is added as an upper bound. With the help of this upper bound, responsiveness and degree of helping the user to focus on the performance improvement can be analyzed. As can be seen, for each threshold value, average number of mismatch patterns \textit{with performance indicator clustering} are very low compared to \textit{without clustering}. In other words, when user wants to improve its performance with any threshold, there is significantly less number of mismatch patterns on average to check. This shows the methodology proposed in this study can help users to focus on differences between organizations given this dataset.
\end{itemize}

>>>>

In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise. In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators. In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster. In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization. As the similarity between process models decreases our method spots more mismatch patterns and it ensures that the developed mismatch pattern analyzers work as expected for this dataset. In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}. 
\begin{figure}[t!]
    	\centering
    	\includegraphics[width=\textwidth]{5_results_discussions/loan-application-process/recommendation-generation-analysis}
    	\caption{Recommendation Generation analysis for Loan Application Process dataset}
      \label{fig:loan-recommendation-generation-analysis}
\end{figure}
In order to construct the data in Figure~\ref{fig:loan-recommendation-generation-analysis}, every organization is selected one-by-one with different threshold values. For each analysis, number of performance indicators and average number of mismatch patterns causing them are plotted. In addition, total number of mismatch patterns without clustering is added as an upper bound. With the help of this upper bound, responsiveness and degree of helping the user to focus on the performance improvement can be analyzed. As can be seen, for each threshold value, average number of mismatch patterns \textit{with performance indicator clustering} are very low compared to \textit{without clustering}. In other words, when user wants to improve its performance with any threshold, there is significantly less number of mismatch patterns on average to check. This shows the methodology proposed in this study can help users to focus on differences between organizations given this dataset.
